Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-08 longSC.tex
small update on figure and abstract

The temperature dependence of $\eta/s$ has some generic features that most known fluids obey. For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n$=2 or 3).
$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
The higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as measured the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparisons to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Various theoretical models used in this article are described in Sec.~\ref{sec:theory}. Sec.~\ref{sec:summary} summarizes our findings.

@@

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}. However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.

\section{Data Analysis}
\label{sec:experiment}
Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effect of jets on the measured correlations. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e, tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution. The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).

As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8cm and was found to be less than 3\%.

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematical errors are represented with boxes.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).

@@

It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations (SC(3,2) and SC(4,2)) as well as SC(5,2) increase non-linearly towards peripheral collisions.
In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
NSC(5,3) shows the strongest correlation among all harmonics while NSC(5,2) shows a weak centrality dependence.
Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.

>>>>

The temperature dependence of $\eta/s$ has some generic features that most known fluids obey. For instance, one such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparisons to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Various theoretical models used in this article are described in Sec.~\ref{sec:theory}. Finally, Sec.~\ref{sec:summary} summarizes our findings.

@@

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}. However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}. 
%The first theoretical studies of SC observables can be found in Refs.~cite{}

\section{Data Analysis}
\label{sec:experiment}
Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were taken for the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed. The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).

As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematical errors are represented with boxes.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).

@@

It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
